Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Define \Tranterm for T-Abs

    By definition of $\Tranctx$,
    if $\nonterm G$ contains a binding for the name $x$,
    then $\nonterm{GC}$ also contains a binding for that name,
    and its type is precisely $\tranty(\nonterm G \vdash \nonterm{ts})$.
    Thus, we are allowed to use the (derived) core typing rule \textsc{CT-VarW}.
\end{itemize}

>>>>

    By definition of $\Tranctx$,
    if $\nonterm G$ contains a binding for the name $x$,
    then $\nonterm{GC}$ also contains a binding for that name,
    and its type is precisely $\tranty(\nonterm G \vdash \nonterm{ts})$.
    Thus, we are allowed to use the (derived) core typing rule \textsc{CT-VarW}.

  \item \textsc{T-Abs}.
    \begin{align*}
      & \inferrule{\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2 \\\\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2}
                  {\nonterm G \vdash \lambda x : \nonterm{ts}_1. \nonterm{es} : (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2) \\\\
                   \Tranterm(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2)
                   }
                  {\nonterm G \vdash \lambda x : \nonterm{tc}_1. \nonterm{es} : \Pi \gterm x : \nonterm{tc}_1. \nonterm{tc}_2},    \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),       \\
                   &\nonterm{tc}_1 = \tranty(\Gamma \vdash \nonterm{tc}_1), \\
                   &\nonterm{tc}_2 = \tranty(\Gamma , x : \nonterm{tc}_1 \vdash \nonterm{tc}_2), \\
                   &\nonterm{ec} = \tranterm().
    \end{align*}

    The right-hand side here is well-formed.
    Firstly, $\Tranty(\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)$
    produces a derivation tree of the form
    $\nonterm{GC} \vdash \Pi \gterm x : \nonterm{tc}_1. \nonterm{tc}_2 : \star$,
    since the only rule allowing deriving
    $\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2$
    is \textsc{TWF-Arr},
    so it is sufficient to inspect the definition of $\Tranty$ for this rule.
    Then, $\Tranterm(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2)$
    produces a derivation of $\nonterm{GC} , \gterm x : \nonterm{tc}_1 \vdash \nonterm{ec} : \nonterm{tc}_2$.
    These two derivations can then be used as premises for \textsc{CT-Abs},
    which is invoked on the right-hand side.
\end{itemize}
